---
title: "A3"
author: "Tora Mullings"
date: "2/18/2022"
output:
  html_document:
    df_print: paged
---

# Load required libraries.
### tidyverse

```{r}
library(tidyverse)
```


# 1. 

### Read CSV file from Fivethirtyeight's Github repo. Take a subset including the names of the majors.

```{r}
filename <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"

majors <- read.csv(filename, header=TRUE, sep=",")

majors <- subset(majors, select=2)



```

### Use gsub() with regex to clean the data.
```{r}
y <-gsub(pattern = "\"", replacement = "", majors)
y <- gsub(pattern = "\\n", replacement="", y)

z <- str_split(y, ", ")

```

### Loop through the majors, looking for the ones containing the keywords `DATA` or `STATISTICS`.
```{r}
a <- data.frame(as.list(z))


for (i in 1:nrow(a)) {
  m <- a[i,1]
  if (length(grep("DATA", m)) != 0) {
    print(m)
  }
  if (length(grep("STATISTICS", m)) != 0) {
    print(m)
  }
}
```


# 2.

### Input string to be transformed:
```{r}
a <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"'

```

### Regex for cleaning the string
```{r}

x <-a 

b <- gsub('(\n)|(\\[|\\])|[0-9]', '', x)

b <- gsub('(\\s+)', ' ', b)


b <- gsub('\" ', '\", ', b)

c <-paste('c(', b ,')',sep="")
c <- gsub("c\\( ", "c\\(", c)


```


### Finally, use writeLines() to see the raw transformed string.
```{r}
writeLines(c)
```


# 3.
### Describe what the expressions will match.

`(.)\1\1`
```{r}
#1 
z <- c("aabbc", "aba","a\1\1" ,"bcc", "xcccx", "church", "bcb", "ffffffxyzhhhhhhhf", "k", "banana", "eleven")
str_view(z, "(.)\1\1", match=TRUE)

```
This matches any character followed by 2 Start of Header (SOH) characters.



`"(.)(.)\\2\\1"`
```{r}
#2 
z <- c("aabbc", "aba","a\1\1" ,"bcc", "xcccx", 
       "church", "bcb", "fxyzhhhhhhhf", 
       "k", "banana", "eleven", "naabbm",
       "abba", "\"woow\"")
str_view(z, '"(.)(.)\\2\\1"', match=TRUE)

```
This matches any string that contains a 4-character palindrome enclosed by double quotes. In other words, it will match strings that go forward the same as backwards with " on both ends.



`(..)\1`
```{r}
#3
z <- c("aabbc", "aba","a\1\1" ,"bcc", "xcccx", 
       "church", "bcb", "aabjjjj", "hijklmnmn","ffffffxyzhhhhhhhf", 
       "k", "banana", "eleven", "ab\1", "bb\1", "cc", "gfrt\1",
       "abba")
str_view(z, "(..)\1", match=TRUE)

```
This will match any string that contains two characters followed by a SOH character.



`"(.).\\1.\\1"`
```{r}
#4
z <- c("aabbc", "aba","a\1\1" ,"bcc", "xcccx", 
       "church", "bcb", "aabjjjj", "hijklmnmn","ffffffxyzhhhhhhhf", 
       "k", "banana", "eleven", "ab\1", "bb\1", "cc", "gfrt\1",
       "abba", "abaca", "\"abaca\"")

str_view(z, '"(.).\\1.\\1"', match=TRUE)
```
This will match a string enclosed in double quotes with a character that repeats twice with 1 character between each repetition.



`"(.)(.)(.).*\\3\\2\\1"`
This will match a string that contains a substring enclosed within double quotes, that starts with 3 characters, then has any number of random other characters, then has the same first 3 characters mirrored. In other words, the substring is like a palindrome, except the reflection happens after some random characters in between.


# 4. 
### Construct regular expressions to match words that:

Start and end with the same character.
```{r}
x <- c("abc", "aba", "bcc", "bcb", "ffffffxyzhhhhhhhf", "k")
str_view(x, "^(.).*\\1$", match=TRUE)

```


Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r}
y <- c("aabbc", "aba", "bcc", "church", "bcb", "ffffffxyzhhhhhhhf", "k")
str_view(y, ".*(..).*(..).*", match=TRUE)
```


Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r}
z <- c("aabbc", "aba", "bcc", "church", "bcb", "ffffffxyzhhhhhhhf", "k", "banana", "eleven")
str_view(z, ".*(.).*\\1.*\\1.*", match=TRUE)
```
















